\documentclass[12pt]{report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{PhysicsSeniorThesis}
\usepackage{indentfirst}
\usepackage{subfiles} % best to load this package last
\begin{document}
\title{A Covariant Description of the Deuteron and a bunch of other stuff}
\author{A. Student}
\principaladviser{John Doe}
\member{Jane Roe}
\member{Albert Einstein}
%\copyrightfalse
\submitdate{June 2012}

\abstract{
An introduction to the use of Bethe-Salpeter and
quasipotential equations in the description of electron scattering
from the deuteron is provided. The basic formalism and many
technical issues are introduced in the context of a simple scalar
theory. Results for bound-state wave functions and scattering
phases shifts for a variety of quasipotential prescriptions are
presented and qualitative characteristics of these solutions are
discussed. The elastic form factors for the bound state in this
model are calculated using the spectator or Gross equation. The
calculations are then extended to account for the complexities
associated with nucleon spin and results are presented for the
elastic structure functions of the deuteron using the spectator
equation. This calculation is shown to produce a good description
of elastic electron scattering from the deuteron over the range of
momentum transfers for which data are available.
}


\beforepreface
\prefacesection{Acknowledgments}
    I would like to thank...
\afterpreface

\subfile{ch01-intro}
\subfile{ch02-relativistic-wave-eqs}
\subfile{ch03-EM-Interactions}
\subfile{ch04-model-of-deuteron}
\subfile{ch05-conclusion}


\begin{thebibliography}{Bliggs}

\addtocontents{toc}{\vspace*{12pt}}

\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
%
\bibitem{KeisterandPolyzou} B. D. Keister and W. N. Polyzou, Adv. Nucl.
                  Phys. {\bf 20}, 225 (1961).
%
\bibitem{Chung} P. L. Chung, F. Coester, B. D. Keister, and W. N.
                 Polyzou, Phys. Rev. C {\bf 37}, 2000 (1988).
%
\bibitem{BetheSalpeter} E. E. Salpeter and H. A. Bethe, Phys. Rev. {\bf 84},
1232 (1951).
%
\bibitem{Tjon} J. Fleischer and J. A. Tjon, Nucl. Phys. {\bf B84},
375 (1975); Phys. Rev. D {\bf 15}, 2537 (1977); {\bf 21}, 87 (1980).
E. van Faassen and J. A. Tjon, Phys. Rev. C {\bf
28},2354 (1983); {\bf 30}, 285 (1984); {\bf 33}, 2105 (1986).
%
\bibitem{Zuilhof} M. J. Zuilhof and J. A. Tjon, Phys. Rev. C {\bf 22}, 2369
            (1980); {\bf 24}, 736 (1981).
%
\bibitem{Umnikov} A. Yu. Umnikov and F. C. Khanna, Phys. Rev. C {\bf 49}
                2311 (1994).
%
\bibitem{BSLT} R. Blankenbecler and R. Sugar, Phys. Rev. {\bf 142}, 1051
               (1966); A. A. Logunov and A. N. Tavkhelidze, Nuovo Cimento
               {\bf 29}, 380 (1963).
%
\bibitem{Thompson} R. H. Thompson, Phys. Rev. D {\bf 1}, 1738 (1970).
%
\bibitem{Todorov} I. T. Todorov, Phys. Rev. D {\bf 10}, 2351 (1971).
%
\bibitem{Erkelenz} K. Erkelenz and K. Holide, Nucl. Phys. {\bf A194},
                  161 (1972).
%
\bibitem{Kadychevsky} V. G. Kadychevsky, Nucl. Phys. {\bf B6}, 125 (1968).
%
\bibitem{GrossA} F. Gross, Phys. Rev. {\bf 186}, 1448 (1969); Phys. Rev. D  {\bf 10},
               223 (1974).
%
\bibitem{GrossB} F. Gross,Phys. Rev. C {\bf 26}, 2203 (1982).
%
\bibitem{FVOHA} F. Gross, J.~W.~Van~Orden and K.~Holinde, Phys. Rev. C {\bf 41},
                R1909 (1990).
%
\bibitem{FVOHB} F. Gross, J.~W.~Van~Orden and K.~Holinde, Phys. Rev. C {\bf 45},
                 2094 (1992).
%
\bibitem{BuckandG} W. W. Buck and F. Gross, Phys. Rev. D {\bf 20}, 2361
%
\bibitem{ACG} R. E. Arnold, C. E. Carlson, and F. Gross, Phys. Rev. C
                   {\bf21}, 2361 (1980).
%
\bibitem{Hummel} E. Hummel and J. A. Tjon, Phys. Rev. Lett. {\bf 63},
1788 (1989).
%
\bibitem{WallaceandM} S. J. Wallace and V. B. Mandelzweig, Nucl. Phys.
                     {\bf A503}, 673 (1989).
%
\bibitem{DevineandW} N. K. Devine and S. J. Wallace, Phys. Rev. C {\bf 48}, 973
                     (1993).
%
\bibitem{Zhu} X. Zhu, R. Gourishankar, F. C. Khanna, G. Y. Leung, and
              N. Mobed, Phys. Rev. C {\bf 45}, 959 (1992).
%
\bibitem{Fuda} M. G. Fuda, Phys. Rev. D {\bf 44}, 1880 (1991).
%
\bibitem{Karmanov} V. A. Karmanov and A. V. Smirnov, Nucl. Phys. {\bf A546},
                691 (1992).
%
\bibitem{Lurie} D. Lurie, {\it Particles and Fields}, (Wiley-Interscience,
         London, 1968).
%
\bibitem{CoesterandRiska} F. Coester and D. O. Riska, Preprint nucl-th
           9309026.
%
\bibitem{BrownandJ} G. E. Brown and A. D. Jackson, {\it The
Nucleon--Nucleon Interaction} (North--Holland, Amsterdam, 1976).
%
\bibitem{GrossBook} F. Gross, {\it Relativistic Quantum Mechanics and Field
            Theory} (Wiley-Interscience, New York, 1993).
%
\bibitem{GrossandRiska} F. Gross and D. O. Riska, Phys. Rev. C {\bf 36}, 1928
(1987).
%
\bibitem{WardTakahashi} J. C. Ward, Phys. Rev. {\bf 78}, 182 (1950);
                Y. Takahashi, Nuovo Cimento {\bf 6}, 371 (1957).
%
\bibitem{ArndtandRoper} R. A. Arndt and L. D. Roper, Scattering Analysis and
Interactive Dial-in (SAID) program, Virginia Polytechnic Institute
and State University.
%
\bibitem{Gals71}S.~Galster, H.~Klein, J.~Moritz, K.~H.~Schmidt, and
D.~Wegener, Nucl. Phys. {\bf B32}, 221 (1971).
%
\bibitem{ItoGross} H. Ito and F. Gross, Phys. Rev. Lett. {\bf 71}, 2555 (1993).



\end{thebibliography}

\subfile{appendix}



\newpage
\vita{This is where I tell you about my academic background and list all of my
accomplishments.}

\vitapage



\end{document}
